Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2018-12-16 paper.tex
Add figures for paper and SI

%\usepackage{xr}
%\externaldocument{SI_v112818}
\usepackage{xr-hyper} 
%\usepackage{zref-xr}
\externaldocument{SI_v120518}

@@

{\bfseries Dielectric constant, which defines the polarization of the media, is a key quantity in condensed matter. It determines several electronic and optoelectronic properties important for a plethora of modern technologies from computer memory to field effect transistors and communication circuits. Moreover, the importance of the dielectric constant in describing electromagnetic interactions through screening plays a critical role in understanding fundamental molecular interactions. Here we show that despite its fundamental transcendence, the dielectric constant does not define unequivocally the dielectric properties of two-dimensional (2D) materials due to the locality of their electrostatic screening. We found instead that the electric polarizability correctly captures the dielectric nature of a 2D material which is united to other physical quantities in an atomically thin layer. We reveal a long-sought universal formalism where electronic, geometrical and dielectric properties are intrinsically correlated through the polarizability opening the door to probe quantities yet not directly measurable including the real covalent thickness of a layer. We unify the concept of dielectric properties in any material dimension finding a global dielectric anisotropy index defining their controllability through dimensionality. 
}

The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
plays a crucial role in bridging various fundamental material
properties, such as bandgaps, optical absorption, and conductivities,   
with elemental interactions, e.g. the electron-electron forces. 
The central place of $\varepsilon$ in physics drives the analysis of several phenomena 
where is common to classify a material accordingly to its ability to screen an electric field $\boldsymbol{E}$ 
in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
condensed matter physics, as well as in related fields in chemistry and materials science. 
The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
theoretical and experimental techniques of distinct flavors where the probe of the dielectric properties 
is made through an external electric field. 

@@

may represent their dielectric features or it can be used as an 

@@

We approach to this problem showing 
that the current definition used in layered materials is ill defined as illustrated in Figure \ref{fig-1}.  
From the theoretical point of view, 
an isolated 2D material is placed in the xy-plane of a  %cutting started here! 

@@

z-direction separating the cell images. The static macroscopic dielectric
tensor from the superlattice $\varepsilon_{\mathrm{SL}}^{pq}$, is
determined through fundamental electrostatics by the response of the
polarization density $\boldsymbol{P}^{p}$ under small perturbative
external field $\boldsymbol{E}^{q}$, where $p$, $q$ are the directions
of polarization and electric field,

@@

$\boldsymbol{u}$ is the total dipole moments within the SL, $\rho$ is the
spatial charge density, $\Omega=AL$ is the volume of the supercell, $A$ is the xy-plane
area of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the
majority of 2D nonmetals, the off-diagonal elements of the
dielectric tensor ($p \neq q$) tend to be negligible.  Considering
that the 2D material is placed in vacuum ($\kappa^{pp} = 1$ and
$\kappa^{pq} = 0$), we can distinguish two components, namely the
in-plane ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane

@@

$\varepsilon_{\mathrm{SL}}^{\perp} =
\varepsilon_{\mathrm{SL}}^{zz}$. 
The absence of bonding perpendicular
to the plane confines the induced dipoles along the
\textit{z}-direction as the charge density difference, $\Delta \rho=\rho(\boldsymbol{E}) - \rho(0)$,
at zero and finite electric fields ($|\boldsymbol{E}_{}|=0.01 \mathrm{V\cdot \AA}^{-1}$) 
extends to $\sim{}$12 \AA{} deeply into the vacuum (Figure \ref{fig-1}{\bf a}). When $L$ is large enough,   
the induced dipoles $\boldsymbol{u}$ from the periodic images do not interact mutually 
as the integral in Eq. \ref{eq:def-eps-2} depends only locally on the atomic charge density at the layer. 
However, we can see from Eqs. \ref{eq:def-eps-1} that both

@@

$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$ via the volume of the cell $\Omega$. 
Therefore, any calculation performed using such definition will intrinsically depend on the magnitude of $L$ as an additional parameter. 
This dependence can be clearly demonstrated by

@@

theory (DFT) using hybrid functionals (see {\it Methods} for details) as a function 
of $L$ for P$\bar{6}$m2 transitional metal dichalcogenides 
(TMDCs), 2H-MX$_{2}$, where M=Mo, W and X=S, Se,
Te (top panels of Figure \ref{fig-1}{\bf b} and \ref{fig-1}{\bf c}, respectively). 
Despite of the magnitudes of $L$ both components of the dielectric constant 
change systematically without a clear convergence.  

@@

Simulations performed at higher levels of theory using 
many-body techniques, G$_{\rm 0}$W$_{0}$ (Supplementary Figure \ref{fig:S1}), 
and also taking into account  electron-hole excitations at the level of the Bethe-Salpeter equation 
at the frequency-dependent versions of $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$
invariably give alike results (Supplementary Figure \ref{fig:S2}). 
Indeed, the variations observed in peak positions at different values of $\omega(eV)$ 
implicate that several other related quantities, such as, the optical absorption and 
optical conductivity, suffer the same deficiencies. In a fully first-principles theory 
such intrinsic dependence on $L$ should not be present. 

@@

It is worth mentioning that experimental results also need to define an effective thickness of the sheet 
to interpret ellipsometry data \cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, 
reflectance or transmission spectra \cite{Li_2014, Yoffe-Wilson69} in 
order to extract information for the real part of the dielectric functions. 
We argue that such procedure may induce inevitably variations of the results as the 
thickness is normally chosen by the interlayer spacing of the 
respective bulk materials (Supplementary Section \ref{sec:2D-3D-rescale} gives an exhaustive analysis).  

@@

To solve this problem, we need to
find the $L$-independent alternative of
$\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
Eq. \ref{eq:def-eps-2} with $L$ we obtain the sheet polarization density
$\boldsymbol{\mu}_{\mathrm{2D}}$, that is, 
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, 
which is independent of $L$ due to the locality 
of $\boldsymbol{u}$ and $A$. 
%
Similar to the definition of molecular
polarizability \cite{Israelachvili_2011},
$\boldsymbol{\mu}_{\mathrm{2D}}$ is associated with the 2D
polarizability $\alpha_{\mathrm{2D}}$ through:
$\boldsymbol{\mu}^{p} = \sum_{q} \alpha_{\mathrm{2D}}^{pq}
\boldsymbol{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
$\boldsymbol{E}_{\mathrm{loc}}$ is the local electric field. 
Using electrostatic boundary conditions, 
the continuity of the electric field along the
in-plane direction gives
$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$
\cite{Markel_2016}. For the out-of-plane component, the dipole
screening yields
$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
\cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D polarizabilities,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
%
%
\begin{subequations}
\begin{eqnarray}
  \label{eq:alpha-para-def}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0}L}\\
  \label{eq:alpha-perp-def}
  &\varepsilon_{\mathrm{SL}}^{\perp} &= \left(1 - {\displaystyle \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{\mathrm{0}} L}} \right)^{-1}
\end{eqnarray}
\end{subequations}
%
%
The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$, calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}. We observe
that both $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ reached 
convergence in a much shorter vacuum length within 10 \AA ~and 15 \AA, respectively. 
%
%
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} 
to reproduce the trends noticed in the top panels in Fig.\ref{fig-1}{\bf b} and \ref{fig-1}{\bf c}  
for $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around 
a centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ 
and $\alpha_{\mathrm{2D}}^{\perp}$ (Fig. \ref{fig-1}{\bf d-e}). 
A similar curve profile is obtained in both components of the dielectric constant including the much 
abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
interlayer interactions.  Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can also be used to remove 
the dependence of $L$ on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ via $\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$, respectively (Supplementary Figure \ref{fig:S3}). 
%
% 
% 
% 
% 
These findings provide that the 2D polarizability captures the essence of the dielectric properties 
of layered materials as the microscopic quantity in describing the 
atomic interactions present in the layers. Its local nature removes any dependence on size effects 
present in the calculations.  
More discussions about the choice of the 2D polarizability
and comparison with other methods can be found in Supplementary Section \ref{sec:2D-3D-rescale}.

@@

where $E_{\mathrm{g}}$ is the minimal electronic bandgap, 
$\delta$ is the intrinsic or covalent thickness of the layer (Fig. \ref{fig-1}{\bf a}), and $C^{\parallel} = {8\pi^{2}\varepsilon_0\AA}/{eN}$, where $N$ corresponds to the degeneracy of the bands associated with $E_{\mathrm{g}}$,
and $C^{\perp} = {1}/{4\pi}$.  Despite of the simplicity of Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}, 
they generalize a direct relationship between the polarizability and the electronic and structural properties for any 
2D material in a new framework. 
We can show that these equations are valid for the current library of known layered materials 
involving different lattice symmetry, element composition, optical and electronic properties. 

@@

showed that our method enables full correlation between these disparate variables. 

@@

Figure \ref{fig-3}{\bf b}
shows the calculated $E_{\mathrm{g}}$ (blue dots) and polarizabilities
(bar plots) of all the 2D materials investigated, covering a wide
spectrum range from far-infrared to ultraviolet at HSE06 level. 
Note from dimension
analysis, it is more intuitive to express the polarizability as

@@

descending trend when $E_{\mathrm{g}}$ increases, while 
no apparent correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and

@@

\ref{sec:pol-2D-Eg}). It is worth mentioning that materials with elements 
having large polarizabilities, such as Hf and Zr in 1T-HfO$_2$ or 1T-ZrO$_2$, 
respectively, also transfer alike features for the layers with slightly variations between 
1T and 2H phases. The former normally shows larger values of $\alpha_{\mathrm{2D}}^{\parallel}$ 
than the latter. 

@@

We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
%
%
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}{\bf d} inset). 
%
%
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and a slope very close to $1/4\pi$ (Figure \ref{fig-3}{\bf d}). 
This results that $\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0} \approx
\delta_{\mathrm{cov}}$ has a strong physical meaning through the geometry of the layer. 
Similar
to the molecular polarizability which characterizes the volume of
electron cloud of an isolated molecule \cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the electron cloud thickness of the 2D
material (see Supplementary Section \ref{sssec:theory-3}). Indeed,
the universal scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in
Figure \ref{fig-3}{\bf d} indicates that the quantity
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
electronic approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, is in reality the
(dielectric) characteristic thickness of a 2D material, and can be
used to resolve the long-existing controversy about the experimental
thickness of 2D materials, such as graphene \cite{Shearer_2016}.
%
To rule out the possibility that our conclusion are limited by the
number of materials used at HSE06, we further 
validate Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
using a different database\cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 compounds calculated at the PBE level, and
superimpose with our results in Figure \ref{fig-3}{\bf c} and \ref{fig-3}{\bf d}
(see details in Supplementary Section \ref{sec:gpaw-1}). Although the
dielectric properties may be overestimated at PBE level due to
underestimation of the bandgap compared with the more accurate HSE06
functionals \cite{Van_Dyck_2017}, similar linear trends can be
observed for both $\alpha^{\parallel}_{\mathrm{2D}}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ with the linear coefficient very close
to the HSE06 results (see details in Supplementary Section
\ref{sec:gpaw-2}).

>>>>

%\usepackage{xr}
\usepackage{xr-hyper} 
\externaldocument{SI}

@@

{\bfseries The dielectric constant, which defines the polarization of
  the media, is a key quantity in condensed matter. It determines
  several electronic and optoelectronic properties important for a
  plethora of modern technologies from computer memory to field effect
  transistors and communication circuits. Moreover, the importance of
  the dielectric constant in describing electromagnetic interactions
  through screening plays a critical role in understanding fundamental
  molecular interactions. Here we show that despite its fundamental
  transcendence, the dielectric constant does not define unequivocally
  the dielectric properties of two-dimensional (2D) materials due to
  the locality of their electrostatic screening. We found instead that
  the electric  polarizability correctly
  captures the dielectric nature of a 2D material which is united to
  other physical quantities in an atomically thin layer. We reveal a
  long-sought universal formalism where electronic, geometrical and
  dielectric properties are intrinsically correlated through the
  polarizability opening the door to probe quantities yet not directly
  measurable including the real covalent thickness of a layer. We
  unify the concept of dielectric properties in any material dimension
  finding a global dielectric anisotropy index defining their
  controllability through dimensionality.  }

The dielectric constant $\varepsilon$ (also known as the relative
permittivity) plays a crucial role in bridging various fundamental
material properties, such as bandgaps, optical absorption, and
conductivities.  \todo{Add more citations} $\varepsilon$ characterizes
the ability to screen an electric field $\boldsymbol{E}$ which
classifies metals, semiconductors and insulators.  \todo[inline]{I
  shortened the sentences. However, can we really "classify" the
  material only by $varepsilon$? For instance HfO2 has large
  $\varepsilon$ but also large bandgap}
% Such definitions determine a broad range of
% condensed matter physics, as well as in related fields in chemistry
% and materials science.
The ability to compute and measure
$\varepsilon$ in bulk materials is well established via different
theoretical and experimental techniques of distinct flavors where the
probe of the dielectric properties is made through an external
electric field.

@@

may represent their dielectric features or only an 

@@

We approach this problem showing that the current definition of
$\varepsilon$ used in layered materials is ill defined as illustrated
in Figure \ref{fig-1}.  From the theoretical point of view, an
isolated 2D material is placed in the \textit{xy}-plane of a

@@

\textit{z}-direction separating the cell images. The static macroscopic
dielectric tensor from the superlattice
$\varepsilon_{\mathrm{SL}}^{pq}$, is determined through fundamental
electrostatics by the response of the polarization density
$\boldsymbol{P}^{p}$ under small perturbative external field
$\boldsymbol{E}^{q}$, where $p$, $q$ are the directions of
polarization and electric field,

@@

$\boldsymbol{u}$ is the total dipole moments within the SL, $\rho$ is
the spatial charge density, $\Omega=AL$ is the volume of the
supercell, $A$ is the \textit{xy}-plane area of the SL and
$\varepsilon_{0}$ is vacuum permittivity. Here we only study the
electronic contribution to the dielectric constant where the dipole
$\boldsymbol{P}$ comes from the displacement of electron cloud under
external electric field. For the majority of 2D nonmetals, the
off-diagonal elements of the dielectric tensor ($p \neq q$) tend to be
negligible \todo[inline]{why only nonmetals?  Could you cite one
  reference?}.  Considering that the 2D material is placed in vacuum
($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can distinguish two
components, namely the in-plane
($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane

@@

$\varepsilon_{\mathrm{SL}}^{\perp} = \varepsilon_{\mathrm{SL}}^{zz}$.
The absence of bonding perpendicular to the plane confines the induced
dipoles along the \textit{z}-direction as the charge density
difference, $\Delta \rho=\rho(\boldsymbol{E}) - \rho(0)$, at zero and
finite electric fields
($|\boldsymbol{E}_{}|=0.01 \mathrm{V\cdot \AA}^{-1}$) extends to
$\sim{}$12 \AA{} deeply into the vacuum (Figure \ref{fig-1}{\bf
  a}). When $L$ is large enough, the induced dipoles $\boldsymbol{u}$
from the periodic images do not interact mutually as the integral in
Eq. \ref{eq:def-eps-2} depends only locally on the atomic charge
density at the layer.  However, we can see from
Eqs. \ref{eq:def-eps-1} that both

@@

$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$ via the volume of
the cell $\Omega$.  Therefore, any calculation performed using such
definition will intrinsically depend on the magnitude of $L$ as an
additional parameter.  This dependence can be clearly demonstrated by

@@

theory (DFT) using hybrid functionals (see {\it Methods} for details)
as a function of $L$ for P$\bar{6}$m2 transitional metal
dichalcogenides (TMDCs), 2H-MX$_{2}$, where M=Mo, W and X=S, Se, Te
(top panels of Figure \ref{fig-1}{\bf b} and \ref{fig-1}{\bf c},
respectively).  Despite of the magnitudes of $L$ both components of
the dielectric constant change systematically without a clear
convergence.

@@

Simulations performed at higher levels of theory using many-body
techniques, G$_{\rm 0}$W$_{0}$ (Supplementary Figure \ref{fig:S1}),
and also taking into account electron-hole excitations at the level of
the Bethe-Salpeter equation (BSE) for the frequency-dependent
$\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ invariably give alike
results (Supplementary Figure \ref{fig:S2}). Moreover, due to the long
range Coulomb interaction, variations of the quasi-particle energy
(and corresponding peak positions) with lattice constant $L$ at the
G$_{0}$W$_{0}$ level is observed (details see Supplementary Section
SXX). Such results implicate that several other related quantities,
including the optical absorption and optical conductivity, suffer the
same deficiencies, which should be avoided in a fully first principles
theory.

@@

It is worth mentioning that experimental dielectric results of 2D
materials generally need to define an ``effective thickness'' of the sheet
to interpret ellipsometry data
\cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, reflectance or
transmission spectra \cite{Li_2014, Yoffe-Wilson69} in order to
extract information for the real part of the dielectric functions.  We
argue that such procedure may induce inevitably variations of the
results as the thickness is normally chosen by the interlayer spacing
of the respective bulk materials (details see Supplementary Section
\ref{sec:2D-3D-rescale}).

@@

To solve this problem, we need to
find the $L$-independent alternative of
$\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
Eq. \ref{eq:def-eps-2} with $L$ we obtain the sheet polarization density
$\boldsymbol{\mu}_{\mathrm{2D}}$, that is, 
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, 
which is independent of $L$ due to the locality 
of $\boldsymbol{u}$ and $A$. 
%
Similar to the definition of molecular
polarizability \cite{Israelachvili_2011},
$\boldsymbol{\mu}_{\mathrm{2D}}$ is associated with the 2D
polarizability $\alpha_{\mathrm{2D}}$ through:
$\boldsymbol{\mu}^{p} = \sum_{q} \alpha_{\mathrm{2D}}^{pq}
\boldsymbol{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
$\boldsymbol{E}_{\mathrm{loc}}$ is the local electric field. 
Using electrostatic boundary conditions, 
the continuity of the electric field along the
in-plane direction gives
$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$
\cite{Markel_2016}. For the out-of-plane component, the dipole
screening yields
$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
\cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D polarizabilities,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
%
%
\begin{subequations}
\begin{eqnarray}
  \label{eq:alpha-para-def}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0}L}\\
  \label{eq:alpha-perp-def}
  &\varepsilon_{\mathrm{SL}}^{\perp} &= \left(1 - {\displaystyle \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{\mathrm{0}} L}} \right)^{-1}
\end{eqnarray}
\end{subequations}
%
%
The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$, calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}. We observe
that both $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ reached 
convergence in a much shorter vacuum length within 10 \AA ~and 15 \AA, respectively. 
%
%
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} 
to reproduce the trends noticed in the top panels in Fig.\ref{fig-1}{\bf b} and \ref{fig-1}{\bf c}  
for $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around 
a centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ 
and $\alpha_{\mathrm{2D}}^{\perp}$ (Fig. \ref{fig-1}{\bf d-e}). 
% A similar curve profile is obtained in both components of the dielectric constant including the much 
% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
% interlayer interactions.
\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true. I think it is better not to explicitly mention this.}
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can also be used to remove 
the dependence of $L$ on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ via $\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$, respectively (Supplementary Figure \ref{fig:S3}). 
%
% 
% 
% 
% 
These findings provide that the 2D polarizability captures the essence of the dielectric properties 
of layered materials as the microscopic quantity in describing the 
atomic interactions present in the layers. Its local nature removes any dependence on size effects 
present in the calculations.  
More discussions about the choice of the 2D polarizability
and comparison with other methods can be found in Supplementary Section \ref{sec:2D-3D-rescale}.

@@

where $E_{\mathrm{g}}$ is the minimal electronic bandgap, $\delta$ is
the intrinsic thickness of the layer (Fig. \ref{fig-1}{\bf
  a}), and $C^{\parallel} = \frac{Ne^2}{2 \pi}$, where $N$ corresponds to
the degeneracy of the bands associated with $E_{\mathrm{g}}$, and
$C^{\perp} = {\varepsilon_{0}}$.  \todo[inline]{The previous
  expressions for the coefficients are wrong. Please see the version
  in SI.} Despite of the simplicity of Eqs. \ref{eq:2D-Moss-para} and
\ref{eq:2D-Moss-perp}, they generalize a direct relationship between
the polarizability and the electronic and structural properties for
any 2D material in a new framework.  We can show that these equations
are valid for the current library of known layered materials involving
different lattice symmetry, element composition, optical and
electronic properties.

@@

shows that our method enables full correlation between these disparate variables. 

@@

Figure \ref{fig-3}{\bf b} compares the calculated fundamental bandgap
$E_{\mathrm{g}}$ (blue dots) and 2D electric polarizabilities (bar
plots) of all the 2D materials investigated, covering a wide spectrum
range from far-infrared to ultraviolet.  Note from dimension analysis,
it is more intuitive to express the polarizability as

@@

descending trend when $E_{\mathrm{g}}$ increases, while no apparent
correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and

@@

\ref{sec:pol-2D-Eg}). It is worth mentioning that materials with
elements having large polarizabilities, such as Hf and Zr in
1T-HfO$_2$ or 1T-ZrO$_2$, respectively, also transfer alike features
for the layers with slightly variations between 1T and 2H phases. The
former normally shows larger values of
$\alpha_{\mathrm{2D}}^{\parallel}$ than the latter.
\todo[inline]{sorry but I don't quite get the idea of this
  sentence. In fact HfO2 and ZrO2 have quite low in-plane
  polarizabilities compared with even TiO2. Shall we just remove these
  sentenses? }

@@

We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
%
%
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}{\bf d} inset). 
%
%
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and a slope very close to $1/4\pi$ (Figure
\ref{fig-3}{\bf d}), which agrees well with Eq \ref{eq:2D-Moss-perp}.
This results indicate that $\alpha_{\mathrm{2D}}^{\perp}$ has a strong
physical meaning through the geometry of the layer.  Similar to the
molecular polarizability which characterizes the volume of electron
cloud of an isolated molecule \cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the electron cloud thickness of the 2D
material (see Supplementary Section \ref{sssec:theory-3}). Indeed, the
universal scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in
Figure \ref{fig-3}{\bf d} indicates that the quantity
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
electronic and optical approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM,Pedersen_2016,Klein_2016,Roch_2018},
is in reality the (dielectric) characteristic thickness of a 2D
material, and can be used to resolve the long-existing controversy
about the experimental thickness of 2D materials, such as graphene
\cite{Shearer_2016}.
%
To rule out the possibility that our conclusion are limited by the
number of materials used at HSE06, we further validate
Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using a different
database\cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 compounds calculated at the PBE level, and
superimpose with our results in Figure \ref{fig-3}{\bf c} and
\ref{fig-3}{\bf d} (see details in Supplementary Section
\ref{sec:gpaw-1}). Although the dielectric properties may be
overestimated at PBE level due to underestimation of the bandgap
compared with the more accurate HSE06 functionals
\cite{Van_Dyck_2017}, similar linear trends can be observed for both
$\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$
with the linear coefficient very close to the HSE06 results (see
details in Supplementary Section \ref{sec:gpaw-2}).

We have also searched for additional relations between the 2D
polarizabilities with other physical quantities, including the
effective carrier mass, quantum capacitance (density of states) and
total atomic polarizabilities with no apparent correlations being
found (Supplementary Section \ref{sec:gpaw-3}).  We found however that
Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} have a natural
connection with the screening properties of the layer.
%
In merit of the unit analysis,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length], that is, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
characteristic lengths, respectively. The in-plane screened
electrostatic potential $V(r)$ from a point charge as
a function of distance $r$: 
$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle
    \frac{2
      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulomb potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively. This is analog to the polarizability ellipsoid picture of
molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
Figure \ref{fig:ellipsoid}). The polarizability ellipsoid for a 2D
material is in general ultra flat, with
$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as can be seen from the group 6
TMDCs in Table \ref{tbl:radii}.  Moreover,
$r_{0}^{\parallel}$ is generally larger for a smaller bandgap
semiconductor, which qualitatively explains the inverse proportional
relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$ seen in Eq. \ref{eq:2D-Moss-para}. 
This gives a geometrical interpretation of the bandgap in terms 
of the screening radius of the layer.
